\chapter{Project Stakeholder Management}

This part provides an overview of stakeholder management for this project. Stakeholders are individuals, groups, or organizations that have an interest in the outcome of a project. Managing stakeholders involves identifying who they are, understanding their needs and expectations, and effectively communicating with them throughout the project lifecycle is critical for project success.

\section{Project Team}

The following tables provide detailed information about the project team, including their roles, contact information, and their responsibilities within the project.


    \begin{longtable}{|l|l|l|l|p{6cm}|}
        \caption{Project Team Information} 
        \label{tab:project_team_info} \\
        \hline
        \textbf{Name} & \textbf{Role} & \textbf{Internal/External} & \textbf{Position} \\
        \hline
        \endfirsthead
        \multicolumn{5}{c}%
        {\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
        \hline
        \textbf{Name} & \textbf{Role} & \textbf{Internal/External} & \textbf{Position} \\
        \hline
        \endhead
        \hline \multicolumn{4}{r}{\textit{Continued on next page}} \\
        \endfoot
        \hline
        \endlastfoot
        Tony & Project Manager & Internal & Leader \\
        \hline
        Hillary & Project Sponsor & Internal & Sponsor \\
        \hline
        Karan Goel & Aspiring Project Manager & Internal & Leader \\
        \hline
        Banin Shrestha & Business Analyst & Internal & Team Member \\
        \hline
        Yang & Business Analyst & Internal & Team Member \\
        \hline
        Kushal Rimal & Programmer/Analyst & Internal & Team Member \\
        \hline
        Affan Mehmood & Programmer/Analyst & Internal & Team Member \\
        \hline
        Dipesh Baral & Network Specialist & Internal & Team Member \\
        \hline
        Nora & Network Specialist & Internal & Team Member \\
        \hline
        Ren & Business Analyst & Internal & Team Member \\
        \hline
        Blake & VP of Human Resources & Internal & Sponsor \\
        \hline
        Rose & Human Resource Analyst & Internal & Specialist \\
        \hline
        Tyrian & Financial Analyst & Internal & Specialist \\
        \hline
        Supplier A & System Trainer & External & Supplier \\
        \hline
    \end{longtable}

    \begin{longtable}{|l|l|p{6cm}|}
        \caption{Project Team Contact Information} 
        \label{tab:project_team_contact} \\
        \hline
        \textbf{Name} & \textbf{Email} & \textbf{Contact} \\
        \hline
        \endfirsthead
        \multicolumn{3}{c}%
        {\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
        \hline
        \textbf{Name} & \textbf{Email} & \textbf{Contact} \\
        \hline
        \endhead
        \hline \multicolumn{3}{r}{\textit{Continued on next page}} \\
        \endfoot
        \hline
        \endlastfoot
        Tony & tony@myh.com & Weekly status meetings, email, phone calls \\
        \hline
        Hillary & hillary@myh.com & Weekly status meetings, email, phone calls \\
        \hline
        Karan Goel & karan.goel@myh.com & Weekly status meetings, email, phone calls \\
        \hline
        Banin Shrestha & banin.shrestha@myh.com & Weekly status meetings, email \\
        \hline
        Yang & yang@myh.com & Weekly status meetings, email \\
        \hline
        Kushal Rimal & kushal.rimal@myh.com & Weekly status meetings, email, code reviews \\
        \hline
        Affan Mehmood & affan.mehmood@myh.com & Weekly status meetings, email, code reviews \\
        \hline
        Dipesh Baral & dipesh.baral@myh.com & Weekly status meetings, email \\
        \hline
        Nora & nora@myh.com & Weekly status meetings, email \\
        \hline
        Ren & ren@myh.com & Weekly status meetings, email \\
        \hline
        Blake & blake@myh.com & Monthly status meetings, email, phone calls \\
        \hline
        Rose & rose@myh.com & Email, phone calls \\
        \hline
        Tyrian & tyrian@myh.com & Monthly status meetings, email \\
        \hline
        Supplier A & suppliera@myh.com & Weekly status meetings, email \\
        \hline
    \end{longtable}
    

\section{Project Team Roles and Interests}

The following table details the roles of each team member, their level of authority, and their interests in the project.


\begin{longtable}{|l|l|l|l|}
    \caption{Project Team Roles and Interests} 
    \label{tab:team_roles_interests} \\
    \hline
    \textbf{Name} & \textbf{Project Role} & \textbf{Level of Authority} & \textbf{Interest} \\
    \hline
    \endfirsthead
    \multicolumn{4}{c}%
    {\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
    \hline
    \textbf{Name} & \textbf{Project Role} & \textbf{Level of Authority} & \textbf{Interest} \\
    \hline
    \endhead
    \hline \multicolumn{4}{r}{\textit{Continued on next page}} \\
    \endfoot
    \hline
    \endlastfoot
    Tony & Project Manager & High & Leading \\
    \hline
    Hillary & Project Sponsor & High & Leading \\
    \hline
    Karan Goel & Aspiring Project Manager & High & Leading \\
    \hline
    Banin Shrestha & Business Analyst & Medium & Supportive \\
    \hline
    Yang & Business Analyst & Medium & Supportive \\
    \hline
    Kushal Rimal & Programmer/Analyst & Medium & Supportive \\
    \hline
    Affan Mehmood & Programmer/Analyst & Medium & Supportive \\
    \hline
    Dipesh Baral & Network Specialist & Medium & Supportive \\
    \hline
    Nora & Network Specialist & Medium & Supportive \\
    \hline
    Ren & Business Analyst & Medium & Supportive \\
    \hline
    Blake & VP of Human Resources & High & Leading \\
    \hline
    Rose & Human Resource Analyst & Medium & Supportive \\
    \hline
    Tyrian & Financial Analyst & Medium & Supportive \\
    \hline
    Supplier A & System Trainer & Medium & Supportive \\
    \hline
\end{longtable}

\begin{longtable}{|p{2.3cm}|p{1.6cm}|p{3cm}|p{3cm}|p{4cm}|}
    \caption{Stakeholder Management Information} 
    \label{tab:stakeholder_management} \\
    \hline
    \textbf{Stakeholder} & \textbf{Role} & \textbf{Most Important Goal} & \textbf{How will he/she contribute} & \textbf{Best way to manage} \\
    \hline
    \endfirsthead
    \multicolumn{5}{c}%
    {\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
    \hline
    \textbf{Stakeholder} & \textbf{Role} & \textbf{Most Important Goal} & \textbf{How will he/she contribute} & \textbf{Best way to manage} \\
    \hline
    \endhead
    \hline \multicolumn{5}{r}{\textit{Continued on next page}} \\
    \endfoot
    \hline
    \endlastfoot
    Hillary & Project Sponsor & Ensure that the MYH Recreation and Wellness System meets the needs of the business and its users. & Will provide support and resources to the project team and approve key decisions. & Keep the project sponsor informed of the project's progress and any potential roadblocks. Regularly seek the project sponsor's input and feedback. \\
    \hline
    Gayle & VP of Human Resources & Ensure that the MYH Recreation and Wellness System meets the needs of the human resources department. & Will provide input on the system's requirements and help to promote the system to employees. & Keep Gayle informed of the progress of the project and seek her input on any aspects of the system that may impact the human resources department or its employees. \\
    \hline
    Supplier A & Training and Incentives Provider & Provide training on the MYH Recreation and Wellness System to employees and manage the incentives program. & Will develop and deliver training materials and manage the incentives program. & Work with Supplier A to develop a training plan and incentives program that meets the needs of the project. Regularly communicate with Supplier A to ensure that the training and incentives program are on track. \\
    \hline
    Employees & Full-Time and Part-Time Employees & Use the MYH Recreation and Wellness System to improve their health and well-being. & Will use the system to track their fitness goals, participate in wellness programs, and earn incentives. & Communicate with employees about the benefits of using the system and provide them with support and training. Regularly collect feedback from employees on the system and use it to make improvements. \\
    \hline
\end{longtable}


\FloatBarrier
\newpage